Cheminformatics: The Computer Science of Chemical Discovery

### 2011-11-13 paper.tex
some fixes to the bibliogrpahy. rephrased conclusions

There is an admittedly steep learning curve, as significant domain
knowledge is required to attack problems of significance. Indeed, many
issues faced by chemists are often detailed and subtle and do not
admit as clean an abstraction as ``algorithms on a string'', the way
many bioinformatics algorithms can be abstracted into a computer
science framework.  As a result, while one can certainly make
significant contributions to cheminformatics by just considering
structures as graphs, one is limited to somewhat abstract
problems. Keeping in mind that cheminformatics is fundamentally a
practical field that serves to help and advance experimental
chemistry, the key challenges require an understanding of the
underlying chemical systems. One could certainly study for a degree in
chemistry. Alternatively one could collaborate with a chemist or
cheminformatics practitioner.

>>>>

There is an admittedly steep learning curve, as significant domain
knowledge is required to attack many problems in cheminformatics due
to the underlying chemistry of the systems being studies. Indeed, many
issues faced by chemists are often detailed and subtle and do not
admit as clean an abstraction as ``algorithms on a string'', the way
many bioinformatics algorithms can be abstracted into a computer
science framework.  As a result, while one can certainly make
significant contributions to cheminformatics by just considering
structures as graphs, one is limited to somewhat abstract
problems. Keeping in mind that cheminformatics is fundamentally a
practical field that serves to help and advance experimental
chemistry, the key challenges require an understanding of the
underlying chemical systems. One could certainly study for a degree in
chemistry. Alternatively one could collaborate with a chemist or
cheminformatics practitioner.
